Windowed least-squares model reduction for dynamical systems

### 2019-10-11 section4/numerical_methods.tex
fixed en dahshes

In the present context, we investigate both direct and indirect methods to solve \methodAcronym\ with \spatialAcronym\ trial
subspaces. We consider: 
\begin{itemize} \item \textit{Direct methods (discretize-then-optimize)}: A direct approach leveraging linear multistep methods to directly solve the optimization problem~\eqref{eq:tclsrm}.
\item \textit{Indirect methods (optimize-then-discretize)}: An indirect approach leveraging the forward-backward sweep algorithm to solve the Euler--Lagrange equations~\eqref{eq:lspg_continuous}-\eqref{eq:lspg_bcs}.

\end{itemize} 
We emphasize that a variety of other approaches exist. Future work will comprise a detailed exploration
of additional approaches.
Section~\ref{sec:direct}  outlines direct solution approaches based on linear
multistep methods, while Section~\ref{sec:indirect} outlines the indirect
solution approach.

>>>>

In the present context, we investigate both direct and indirect methods to solve \methodAcronym\ with \spatialAcronym\ trial
subspaces. We consider: 
\begin{itemize} \item \textit{Direct methods (discretize-then-optimize)}: A direct approach leveraging linear multistep methods to directly solve the optimization problem~\eqref{eq:tclsrm}.
\item \textit{Indirect methods (optimize-then-discretize)}: An indirect approach leveraging the forward--backward sweep algorithm to solve the Euler--Lagrange equations~\eqref{eq:lspg_continuous}-\eqref{eq:lspg_bcs}.

\end{itemize} 
We emphasize that a variety of other approaches exist. Future work will comprise a detailed exploration
of additional approaches.
Section~\ref{sec:direct} outlines a direct solution approach based on linear
multistep methods, while Section~\ref{sec:indirect} outlines an indirect
solution approach based on the forward--backward sweep algorithm.

### 2019-10-11 section4/spatial_numerical.tex
fixed en dahshes

define the specific type of multistep scheme. Examples of linear multistep schemes include Adams-Bashforth schemes and  
Adams-Moulton schemes. 

@@

\subsection{\spatialAcronym: indirect solution approach}\label{sec:indirect}
In contrast to the direct approach,
indirect methods ``indirectly" solve the minimization
problem~\eqref{eq:tclsrm} by solving the Euler--Lagrange equations. The
system given by the Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_adjoint} comprises a coupled two-point boundary value
problem. A variety of techniques have
been devised to solve two-point boundary value problems of this type. These
techniques include shooting methods, multiple shooting
methods~\cite{multiple_shooting}, and the forward-backward sweep
method~\cite{fbs} (FBSM).  This work explores using the FBSM.

@@

\subsubsection{Forward-backward sweep method (FBSM)}\label{sec:FBSM}
%\subsubsection{Solution Strategy} Solving Eq.~\ref{eq:lspg_continuous} is
%made challenging by the fact that it is a coupled two-point boundary value
%problem. The forward problem is coupled to the backwards adjoint problem,
%while the backwards adjoint sytem is coupled to the forward problem. The
%problem is thus inherently implicit. The most popular techniques to solve
%these types of two-point boundary value problems are shooting methods,
%multiple shooting methods, fully-implicit methods, and the forward backward
%sweep (FBS) method. This work explores using the FBS method.

@@

\begin{remark}\label{remark:fbsm}(Acceleration of Indirect Methods)
The FBSM is a simple iterative method for solving the coupled two-point boundary value problem. For large time windows, however, the FBSM may require many 
forward-backward iterations for convergence. More sophisticated solution techniques, such as a multiple FBSM method or multiple shooting methods, promise 
to reduce this cost. Analyses of additional solution techniques will be a subject of future work.
\end{remark}

>>>>

define the specific type of multistep scheme. Examples of linear multistep schemes include Adams--Bashforth schemes and  
Adams--Moulton schemes. 

@@

\subsection{\spatialAcronym: indirect solution approach}\label{sec:indirect}
In contrast to the direct approach,
indirect methods ``indirectly" solve the minimization
problem~\eqref{eq:tclsrm} by solving the Euler--Lagrange equations. The
system given by the Euler--Lagrange equations~\eqref{eq:lspg_continuous}--\eqref{eq:lspg_adjoint} comprises a coupled two-point boundary value
problem. A variety of techniques have
been devised to solve two-point boundary value problems of this type. These
techniques include shooting methods, multiple shooting
methods~\cite{multiple_shooting}, and the forward--backward sweep
method~\cite{fbs} (FBSM).  This work explores using the FBSM.

@@

\subsubsection{Forward--backward sweep method (FBSM)}\label{sec:FBSM}
%\subsubsection{Solution Strategy} Solving Eq.~\ref{eq:lspg_continuous} is
%made challenging by the fact that it is a coupled two-point boundary value
%problem. The forward problem is coupled to the backwards adjoint problem,
%while the backwards adjoint sytem is coupled to the forward problem. The
%problem is thus inherently implicit. The most popular techniques to solve
%these types of two-point boundary value problems are shooting methods,
%multiple shooting methods, fully-implicit methods, and the forward backward
%sweep (FBS) method. This work explores using the FBS method.

@@

\begin{remark}\label{remark:fbsm}(Acceleration of Indirect Methods)
The FBSM is a simple iterative method for solving the coupled two-point boundary value problem. For large time windows, however, the FBSM may require many 
forward--backward iterations for convergence. More sophisticated solution techniques, such as a multiple FBSM method or multiple shooting methods, promise 
to reduce this cost. Analyses of additional solution techniques will be a subject of future work.
\end{remark}
